run_analysis
========================================================
```{r sessionInfo, include=TRUE, echo=TRUE, results='markup'}
sessionInfo()
```

This script is for the Coursera course "Getting and Cleaning Data"

Please see readme.md and codebook.md for further details

Created by Garret Wais https://github.com/glw/activity_analysis


# Part 1 of 2 - Download and extract data.

### Large file to be downloaded into a temporary folder within users computer and unzipped into ./data folder

```{r download url}
fileurl = "http://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip"
```

### create temporary directory to hold temporary file

```{r temporary directory}
tempdir = tempdir()
```
 
### create temporary zip file

```{r temporary file}
temp <- tempfile(tmpdir = tempdir, fileext = ".zip")
```

### download file into temp folder

```{r download}
download.file(fileurl, destfile = temp, method = "curl")
```

### create a list of files within zip

```{r list files}
files <- unzip(temp, list=TRUE)
files
```

### if data folder does not exist within the working directory create it, in current working directory.

```{r create dir data}
if (!file.exists("data")){dir.create("data")}
```

### Unzip contents into new data folder within working directory

```{r unzip data}
unzip(temp, exdir = "./data", overwrite = TRUE)
```

### unlink temporary files and directory
```{r unlink}
unlink(temp)
unlink(tempdir)
```

# Part 2 of 2 - Read data and merge test and training sets

    Read tables
```{r}
ytest <- read.table("./data/UCI HAR Dataset/test/y_test.txt", header = F)
xtest <- read.table("./data/UCI HAR Dataset/test/X_test.txt", header = F)
xtrain <- read.table("./data/UCI HAR Dataset/train/X_train.txt", header = F)
ytrain <- read.table("./data/UCI HAR Dataset/train/y_train.txt", header = F)
subjtrain <- read.table("./data/UCI HAR Dataset/train/subject_train.txt", header = F)
colnames(sub)
subjtest <- read.table("./data/UCI HAR Dataset/test/subject_test.txt", header = F)
features <- read.table("./data/UCI HAR Dataset/features.txt", header = F)
activities <- read.table("./data/UCI HAR Dataset/activity_labels.txt", header = F)
```

    Merging datasets
```{r}
X.df <- rbind(xtest, xtrain)

Y.df <- rbind(ytest, ytrain)

Subj.df <- rbind(subjtest, subjtrain)
```

    Keep Columns with "-mean" or "-std"
```{r}
keep_feat <- grep("-mean\\(\\)|-std\\(\\)", features[, 2])
```

    User activities to label Y.df
```{r}
Y.df[,1] = activities[Y.df[,1], 2]
names(Y.df) <- "activity"
```

    Subset X.df with keep_feat and label columns *Used* headers from features to label Final tidy dataset headers 
```{r}
X.df <- X.df[, keep_feat]
names(X.df) <- features[keep_feat, 2]
names(X.df) <- gsub("\\(|\\)", "", names(X.df))
```

    Bind data sets and eport to tidy data file
```{r}
names(Subj.df) <- "Subject"
final_set <- cbind(Subj.df, Y.df, X.df)
write.table(final_set, "tidy_dataset.txt")
```

    Summary: tidy_dataset.txt
```{r}
tidy <- read.table("tidy_dataset.txt")
summary(tidy)
```

    Head: tidy_dataset.txt
```{r}
head(tidy)
```

# Make codebook.
  **Data in this dataset has been divided by its range, normalizing the dataset, ie. it has no units.**
  
  CodeBook.md has been produced...
