run_analysis
========================================================
```{r sessionInfo, include=TRUE, echo=TRUE, results='markup'}
sessionInfo()
```

This script is for the Coursera course "Getting and Cleaning Data"

Please see readme.md and codebook.md for further details

Created by Garret Wais https://github.com/glw/activity_analysis


# Part 1 - Download and extract data.

### Large file to be downloaded into a temporary folder within users computer and unzipped into ./data folder

```{r download url}
fileurl = "http://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip"
```

### create temporary directory to hold temporary file

```{r temporary directory}
tempdir = tempdir()
```
 
### create temporary zip file

```{r temporary file}
temp <- tempfile(tmpdir = tempdir, fileext = ".zip")
```

### download file into temp folder

```{r download}
download.file(fileurl, destfile = temp, method = "curl")
```

### create a list of files within zip

```{r list files}
files <- unzip(temp, list=TRUE)
files
```

### if data folder does not exist within the working directory create it, in current working directory.

```{r create dir data}
if (!file.exists("data")){dir.create("data")}
```

### Unzip contents into new data folder within working directory

```{r unzip data}
unzip(temp, exdir = "./data", overwrite = TRUE)
```

### unlink temporary files and directory
```{r unlink}
unlink(temp)
unlink(tempdir)
```

# Part 2 - Read data and merge test and training sets



# Make codebook.
  Data in this dataset has been divided by its range, normalizing the dataset, ie. it has no units.
  
  CodeBook.md has been produced...
